### 2010-08-17 docs/mg/mg.tex
update the MAC section

  There are 2 tolerances here: a relative tolerance of $\epsilon =
  \mathtt{eps\_mac} \cdot \mathtt{mac\_level\_factor}^{(\mathtt{nlevs}-1)}$, and a bottom
  solver tolerance of $\epsilon_\mathrm{bottom} = \mathtt{eps\_mac\_bottom}$.  These
  parameters are set in {\tt mg\_eps.f90} and have the default values:
   \begin{center}
   \begin{tabular}{ll}
   {\tt eps\_mac}           &= $10^{-10}$ \\
   {\tt mac\_level\_factor} &= 10 \\
   {\tt eps\_mac\_bottom}   &= $10^{-3}$
   \end{tabular}
   \end{center}

>>>>

  There are two tolerances here.  The norm of the residual is required
  to be reduced by a relative tolerance of $\epsilon =
  \min \{ \mathtt{eps\_mac\_max}, \mathtt{eps\_mac} \cdot
  \mathtt{mac\_level\_factor}^{(\mathtt{nlevs}-1)} \}$. A separate
  tolerance is used for the bottom
  solver, $\epsilon_\mathrm{bottom} =
  \mathtt{eps\_mac\_bottom}$.  These parameters are set in {\tt
    mg\_eps.f90} and have the default values:
   \begin{center}
   \begin{tabular}{ll}
   {\tt eps\_mac}           &= $10^{-10}$ \\
   {\tt eps\_mac\_max}           &= $10^{-8}$ \\
   {\tt mac\_level\_factor} &= 10 \\
   {\tt eps\_mac\_bottom}   &= $10^{-3}$
   \end{tabular}
   \end{center}
